Title

### 2017-05-09 paper/paper.tex
added figures

The \texttt{RidgeFair} algorithm was also implemented as presented in (Joseph et al., 2016). This algorithm is very similar in implementation to \texttt{IntervalChaining}, save that it’s narrower confidence intervals allow for derivation of tighter regret bounds. Some details to note are that we assume for simplicity (and without loss of generality) that our parameter $R = 1$ and that we play uniformly randomly among all arms.

@@

We ran experiments that compared the regret of \textsc{IntervalChaining} (IC) with the regret of \textsc{TopInterval} (TI). As in \newcite{DBLP:journals/corr/JosephKMNR16}, we present three sets of empirical results: 
\begin{itemize}
	\item Varying $T$ (the number of rounds) - we measured the average regret of \textsc{IntervalChaining} and \textsc{TopInterval} as a function of increasing $T$.
	\item Varying $k$ (the number of arms/groups) - we measured the average regret of \textsc{IntervalChaining} and \textsc{TopInterval} as a function of increasing $k$.
	\item Varying $d$ (the number of features) - we measured the average regret of \textsc{IntervalChaining} and \textsc{TopInterval} as a function of increasing $d$.
\end{itemize}

For each increasing variable ($T$, $k$, or $d$), we present nine metrics as a function of the variable, each averaged over 500 trials. Contexts are drawn uniformly at random from $[0,1]^d$ and standard Gaussian noise. \newcite{DBLP:journals/corr/JosephKMNR16} only present the average regret difference (metric \#3).
\begin{enumerate}
	\item Average regret (TI) - the average regret of \textsc{TopInterval} across all rounds.
	\item Average regret (IC) - the average regret of \textsc{IntervalChaining} across all rounds.
	\item Average regret difference (TI vs. IC) - the difference between the average regrets of \textsc{TopInterval} and \textsc{IntervalChaining} across all rounds.
	\item Cumulative regret (TI) - the cumulative regret of \textsc{TopInterval} across all rounds.
	\item Cumulative regret (IC) - the cumulative regret of \textsc{IntervalChaining} across all rounds.
	\item Cumulative regret difference (TI vs. IC) - the difference between the cumulative regrets of \textsc{TopInterval} and \textsc{IntervalChaining} across all rounds.
	\item Final regret (TI) - the regret of \textsc{TopInterval} in the final round.
	\item Final regret (IC) - the regret of \textsc{IntervalChaining} in the final round.
	\item Final regret difference (TI vs. IC) - the difference between the final regrets of \textsc{TopInterval} and \textsc{IntervalChaining}.
\end{enumerate}

>>>>

The \texttt{RidgeFair} algorithm was also implemented as presented in \newcite{DBLP:journals/corr/JosephKMNR16}. This algorithm is very similar in implementation to \texttt{IntervalChaining}, save that it’s narrower confidence intervals allow for derivation of tighter regret bounds. A couple small details to note are, first, that we assume for simplicity (and without loss of generality) that the noise is $R$ sub-Gaussian with parameter $R = 1$ and second, that we play uniformly at random among all arms in the set of actions chained to the max.

@@

We ran experiments that compared the regret of \textsc{IntervalChaining} (IC) with the regret of \textsc{TopInterval} (TI). As in \newcite{DBLP:journals/corr/JosephKMNR16}, we present three sets of empirical results: 
\begin{itemize}
	\item Varying $T$ (the number of rounds) - we measured the average regret of \textsc{IntervalChaining} and \textsc{TopInterval} as a function of increasing $T$. (Figure \ref{fig:free_T})
	\item Varying $k$ (the number of arms/groups) - we measured the average regret of \textsc{IntervalChaining} and \textsc{TopInterval} as a function of increasing $k$. (Figure \ref{fig:free_k})
	\item Varying $d$ (the number of features) - we measured the average regret of \textsc{IntervalChaining} and \textsc{TopInterval} as a function of increasing $d$. (Figure \ref{fig:free_d})
\end{itemize}

For each increasing variable ($T$, $k$, or $d$), we present nine metrics as a function of the variable, each averaged over 50 trials. Contexts are drawn uniformly at random from $[0,1]^d$ and standard Gaussian noise. \newcite{DBLP:journals/corr/JosephKMNR16} only present the average regret difference (metric \#3).
\begin{enumerate}
	\item Average regret (TI) - the average regret of \textsc{TopInterval} across all rounds.
	\item Average regret (IC) - the average regret of \textsc{IntervalChaining} across all rounds.
	\item Average regret difference (TI vs. IC) - the difference between the average regrets of \textsc{TopInterval} and \textsc{IntervalChaining} across all rounds.
	\item Cumulative regret (TI) - the cumulative regret of \textsc{TopInterval} across all rounds.
	\item Cumulative regret (IC) - the cumulative regret of \textsc{IntervalChaining} across all rounds.
	\item Cumulative regret difference (TI vs. IC) - the difference between the cumulative regrets of \textsc{TopInterval} and \textsc{IntervalChaining} across all rounds.
	\item Final regret (TI) - the regret of \textsc{TopInterval} in the final round.
	\item Final regret (IC) - the regret of \textsc{IntervalChaining} in the final round.
	\item Final regret difference (TI vs. IC) - the difference between the final regrets of \textsc{TopInterval} and \textsc{IntervalChaining}.
\end{enumerate}

\begin{figure*}[ht!]
	\centering
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_avg_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_avg_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_avg_regret_diff}
	}
	\\
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_cum_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_cum_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_cum_regret_diff}
	}
	\\
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_final_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_final_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{T_50x_final_regret_diff}
	}
	\caption{$d=2$, $k=2$, free $T$}
	\label{fig:free_T}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_avg_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_avg_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_avg_regret_diff}
	}
	\\
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_cum_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_cum_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_cum_regret_diff}
	}
	\\
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_final_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_final_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{k_50x_final_regret_diff}
	}
	\caption{$d=2$, $T=1000$, free $k$}
	\label{fig:free_k}
\end{figure*}

\begin{figure*}[ht!]
	\centering
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_avg_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_avg_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_avg_regret_diff}
	}
	\\
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_cum_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_cum_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_cum_regret_diff}
	}
	\\
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_final_regret_ti}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_final_regret_ic}
	}
	\subfloat{ %
		\includegraphics[width=0.33\textwidth, height=0.33\textheight, keepaspectratio]{d_50x_final_regret_diff}
	}
	\caption{$k=2$, $T=1000$, free $d$}
	\label{fig:free_d}
\end{figure*}
